A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-15 paper/paper.tex
Typo in abstract

\begin{abstract}
    We introduce a new branch and bound algorithm for the maximum common
    subgraph and maximum common connected subgraph problems which is based
    around vertex labelling and partitioning. Our method in some ways resembles
    a traditional constraint programming approach, but uses a novel compact
    domain store and supporting inference algorithms which dramatically reduce
    the memory and computation requirements during search, and allow better
    dual viewpoint ordering heuristics to be calculated cheaply.  Experiments
    show a speedup of more than an order of magnitude over the state of the
    art, and demonstate that we can operate on much larger graphs without
    running out of memory.
\end{abstract}

>>>>

\begin{abstract}
    We introduce a new branch and bound algorithm for the maximum common
    subgraph and maximum common connected subgraph problems which is based
    around vertex labelling and partitioning. Our method in some ways resembles
    a traditional constraint programming approach, but uses a novel compact
    domain store and supporting inference algorithms which dramatically reduce
    the memory and computation requirements during search, and allow better
    dual viewpoint ordering heuristics to be calculated cheaply.  Experiments
    show a speedup of more than an order of magnitude over the state of the
    art, and demonstrate that we can operate on much larger graphs without
    running out of memory.
\end{abstract}
